The assignment document was unclear and ambiguous on some points of the specifications. Hence, we will make the following assumptions:
			
			\begin{itemize}
				\item Parking areas and special parking areas are two different things; however, common sense suggests that it isn't logical to charge users if they plug the car to the power grid in a recharging area but are not parked in a safe area. Neither it makes sense to sanction them if they park it in a safe area that is 3 km far from the power grid. Having the two areas separate would lead to the consequences above, so we decided that while a safe area may not be a recharging area, recharging areas are always safe areas. % not clear the part "Neither it makes sense to sanction them if they park it in a safe area that is 3 km far from the power grid.": I think this can actually happen and was just discussed after this was written: is that correct? :)
				Furthermore, assuming that a city has many safe areas, so that users can enjoy the service all around the city, it is reasonable to think that just a few of them have been equipped with a power grid connection, for economic and infrastructural reasons.
				
				\item The users are able to reserve an available car only from their geographical region. %It wasn't clear from the assignments document whether the user would be able to reserve a specific car; we assume so. %FIXIT actually depends on how Pat decides to formulate her part of the goals
				
				\item There is a "manual" way to close and open the car, i.e. that the user is allowed to temporarily park the car – while still being charged –, get out, close the car, and then get back and open it again. This means that the system can be used not only for one-way travels, but also when more stops or a round trip is needed.
				
				\item Parking areas and special parking areas are allotted and private parking spaces owned by \textit{PowerEnJoy} and distributed throughout the urban area. %discuss.
				
				\item We assume that all cars are the same model and have the same features; specifically, they are all 5-door Citroën C-Zero Micro Car with four seats, customized for the purposes of \textit{PowerEnJoy}. %https://en.wikipedia.org/wiki/Mitsubishi_i-MiEV
				
				\item If there is at least one passenger, the system cannot infer if the driver is actually the user or the user is the passenger and someone else is driving. There is no way of knowing that; however, we assume that upon registration the user has accepted the policy that asks them to be the only driver. If they do not comply to that and commit some infractions, the company reserves the right to take legal action. 
				
				\item The text of the assignment does not say how parking areas are selected when the user has chosen the money saving option. We assume that our clients has given or will give us a computable and feasible algorithm to manage priorities in suggestions and to find the "uniform distribution" of cars. 

			\end{itemize}