We assume that the following properties hold in the analyzed world:			
			
			\begin{itemize}
				\item A tablet is permanently installed in every car. %FIXME tablet??
				\item The tablet is alimented through the car and cannot be switched off.
				\item All cars are equipped and located with a GPS system provided by the tablet.
				\item All GPS systems always give the right position.
				\item GPS tracking is always on.
				\item All cars has sensors to detect the presence of passengers in each seat.
				\item The system is always able to tell how many people occupy a car.
				\item All cars are equipped with a Bluetooth system provided by the tablet.
				\item The Bluetooth system is always on.
				\item All cars are equipped with an integrated alarm as theft deterrent. %XXX never spoke abt that
				\item All cars are equipped with an accident detection system which is always able to notify the company of an accident when the driving user can't. 
				%FIXME other sensors?
				\item A user can provide their location with their phone's GPS whenever they want. 
				\item The safe areas are predefined and within the municipality of Milan.
				\item The payments of all services are managed by an external company, which guarantees fulfillment.
				\item The cars always ignite when they have more than 3\% of power charge.
				\item There is no policy for time limits for a user to retain and use a reserved car. %FIXME rewrite. Also, is this a domain property?? Also, battery runs out??
				\item To complete the registration procedure, the user must send their driving license and ID as pdf documents to the company email address.
				\item If there is at least one passenger, the system cannot infer if the driver is actually the user or the user is the passenger and someone else is driving. There is no way of knowing that; however, we assume that upon registration the user has accepted the policy that asks them to be the only driver. If they do not comply to that and commit some infractions, the company reserves the right to take legal action. %XXX WTH this is not a property. Or is it??
				\item Localization services and maps are provided by an external company, which guarantees precision. 
				
			\end{itemize}