
\subsection{Functional Requirements}
We assume that all domain properties stipulated in paragraph 1.6 hold. Thus we can derive the following functional requirements in order to fulfill the goals listed in paragraph 1.5.

For each goal, we derive the following requirements:

\begin{itemize}
	\item [G1] Registration of a guest to the system.%\textbf{G1} Guest are able to register to the System. Each guest must fill a profile to become a user.
		\begin{itemize}
			\item The system has to allow any person to sign up. %FIXME only from website: must say here?
		\end{itemize}
	\item [G2] Access to the system %\textbf{G2} To complete the procedure of registration the system sends a password to the guest as an access key.
		\begin{itemize}
			\item The system has to send a newly generated password to the user via email when prompted by the admin.
			\item The system must be able to check whether a password is correct or not.
			\item The system must let the user log in only if the password is correct. 
		\end{itemize}
	\item [G3] Finding cars % \item \textbf{G3} The system enables the registered user to find the locations of an available car within a certain distance from the user's location or from a specified address.
		\begin{itemize}
			\item The system must be able to locate the user through their smartphone's GPS.
			\item The system must be able to find a specific address in its map. %FIXME horridly put.
			\item The system must be able to find parking areas in a given area of the map. 
			\item The system must be able to identify available cars inside parking areas.
			\item The system must let users see whether there are available cars in a specified radius. 
		\end{itemize}
	\item [G4] Reservation of a car %The system enables user to reserve a single available car in a certain geographical region for one hour before the user picks it up.
		\begin{itemize}
			\item The system must allow users to reserve an available car.
			\item The cars cannot be reserved by more than one user at any given time.
			\item The system must keep the current reservation standing until the user has opened the car or an hour has passed.
		\end{itemize}
	\item [G5] Fine for not picking up a reserved car. % If the reserved car is not picked up within one hour from the reservation time, the reservation expires and the system tag this car as available. The system charges user a fee of 1 EUR. 
		\begin{itemize}
			\item The system must be able to cancel reservations.
			%TODO others?????
		\end{itemize}
	\item [G6] Opening a car %When the user tells the system that he's near the reserved car, the system unlocks the car to let the user enter.  
		\begin{itemize}
			\item The system should be able to detect when a user is near a reserved car throught the car's Bluetooth system.
			\item The system should be able to unlock a specific car.
		\end{itemize}
	\item [G7] Charging fees to the user %The system charges the user for a predefined amount of money per minute.
		\begin{itemize}
			\item The system must be able to calculate the fee to charge the user.
			\item The system should notify the user of the fee per minute he's being charged.
		\end{itemize}
	\item [G8] Starting charging %The system starts charging the user as soon as the car ignites.
		\begin{itemize}
			\item The system must be able to tell when the car has ignited. 
			\item The system should start counting the charges from the ignition onward. %FIXME horridly put and don't know if a requirement.
		\end{itemize}
	\item [G9] Ending charging %The system stops charging the user when the car is parked in a safe area and the user exits the car. The user must confirm the operation, otherwise the system keeps charging them. 
		\begin{itemize}
			\item The system must be able to tell when the car is parked in a safe area.
			\item The system must be able to detect whether the driver is still in the car.
			\item The system must ask the user whether they wish to end the ride or not; if they decide so, the system should stop charging them, otherwise it should keep doing so. 
		\end{itemize}
	\item [G10] Notification of the current charges %A screen on the car notifies the user of the current charges.
		\begin{itemize}
			\item The system must calculate the charges in real time and show them onscreen. %DAMMIT this is heinous. 
		\end{itemize}
	\item [G11] Locking a car %The system locks the car automatically when the user exits the car inside a safe area.
		\begin{itemize}
			\item The system should be able to lock a specific car without user input. %FIXME is "without user input" correct?
			%all other points (inside safe area and user still inside) already written in [G9]
		\end{itemize}
	\item [G12] 
\end{itemize}



\subsection{Non-functional Requirements}