\subsection{Scenario 1: Registration from the website}
	Anakin has just moved to Milan and has rented a flat; however, he couldn't afford a place close to the city centre, where he works; he also doesn't have a car, so he's been going back and forth with public transport. Because of that, he needs to wake up half an hour earlier and usually gets home very late, and he's getting tired. He then decides to look for a solution on Google, and he finds the car–sharing service of \textit{PowerEnJoy}, which has a parking place close to his home. The \textit{PowerEnJoy} web page has all the information readily available, pricing, features, an approximated map of the parking areas included and a link to download the application from suitable store, so Anakin decides to sign up. He completes a form, where he writes his complete name, personal information, information about his driving license, credentials and payment; the system checks Anakin's driving license and only then sends him the password, so he can login from the phone application and access the private area of the system. 
		
\subsection{Scenario 2: Login in the app} %TODO delete it?
	Padmé has registered on the \textit{PowerEnJoy} website and now has downloaded the application on her smartphone. Opening the application, she finds a screen asking her to log in. Padmé registered with \textit{Naboo\_princess} username, and the password she received in her email is \textit{7aKmm93s}, so she fills the login form with this information. The first time she writes the password wrong, so the login is rejected and the application asks her to try again. The second time she typed the password right, so the system accepts the login and shows the main page of the application.
	
\subsection{Scenario 3: Reserving and using a car}
	Luke must reach his aunt and uncle for the usual sunday roast. He doesn't have a car, and usually he just takes the subway. However today the public transport workers are on strike, and the metro is out of order. Luke is a distracted kid, always with his head in the clouds, so he forgot about the strike and has walked for the fifteen minutes needed to reach the metro. He is nevertheless smart and resourceful, and so he remembers that he's signed in the \textit{PowerEnJoy} system. He opens the app and presses the "find car" button. He has the GPS activated, so the system locates him and tells him that there's a parking area with an available car next to the metro station. The application gives him the choice of reserving the car or cancel the operation, and Luke reserves the car. 
	
\subsection{Scenario 4: Parking and regular fees}
	Leia needs to get to the american consulate ASAP. She's a frequent user of the car–sharing service, so she already knows all the safe areas where she can park around the diplomatic block in the city centre, since she often needs to go there. While she drives, the smart display in her car tells her how much the system is currently charging: the fee per minute is 0,50 EUR, and she's been driving for half an hour, so her fee currently is 15 EUR. She reaches the diplomatic area after two more minutes, and she knows that the parking area is around the corner from the consulate, so she reaches there. This particular safe area is not a recharging area, and Leia left the car with a 40\% battery full, so the system charges her 16 EUR. The display notifies her that she's parked in a safe area and that no sanction or discount applies to her fee. She exits the car and the system locks it automatically. 
	
\subsection{Scenario 5: Power grid and discounted fees}
	Boba Fett has arrived to a recharging area and parks there. He notices that the battery is under 20\%, so he decides to plug the car in the power grid. When he exits the car, the system closes it automatically and notifies him of the time window where he can plug it or reopen it. He plugs the car to the power grid while the time window is still open and then goes his way. After the time window closes, the system detects the car is plugged in and notifies Boba Fett of the final charges, discount for pluggin the car included. 
	
\subsection{Scenario 6: Parking outside safe areas}
	Han, Leia's husband, is also a regular user of the system. He's however less abiding to rules and is a bit of a free spirit, so he generally never gains any discount and is often sanctioned for wasteful behaviour. For example, last monday he needed to reach his bank in Porta Genova for a meeting with his broker. He was very late, so he parked right outside the bank, outside any safe area. It took him twenty minutes to get there, so the system had charged him 10 EUR. As soon as he stops the car, the display notifies him that he is in an unsafe area, so he'll keep being charged even if he isn't using the car. Han confirms and exits. The car doesn't lock automatically, so he needs to turn his bluetooth on and close it with the \textit{PowerEnJoy} application. 

\subsection{Scenario 7: Lost reservation}
	Han and Leia want to go a restaurant. Han thinks that they are about to leave the house, so he decides to reserve a car while still at home to make sure they will have a car after leaving home, but it takes Leia more than an hour to get prepared. In one hour they are not near the car to open it, so the system cancels Han's reservation, notifies him about the 1 EUR sanction charged for uselessly reserving it and asks if he wants to reserve another available car.    	
	
\subsection{Scenario 8: Two passengers + special parking area}
	Chewbacca met Han and Leia on his way, so he invited them to take one car. When they sit in the car, Chewbacca receives a notification on the display that two other passengers are detected. When they arrive to their destination, Chewbacca sees on the application's map that there is a special parking area near them, therefore he decides to put the car there and doesn't forget to plug in the car to the power grid. At the end of the ride Chewbacca gets a discount of 40\% (10\% for the 2 passengers + 30\% for leaving the car on the special parking area and plugging it to the power grid).  
	
\subsection{Scenario 9: Money saving option}
	Lando Calrissian has decided to go to the movies tonight: a new Star Wars movie is out and he heard it's very good. He is not in a hurry, so he reserves a car and decides, once he gets there, that he might as well turn the money saving option on to receive a discount. He inserts his destination in the system and presses enter; the system tells him that he'll need to park the car in a recharging area 0.5 kilometres from the cinema. Lando starts driving and arrives at the recharging area. He then exits the car and the system closes it automatically. He doesn't plug the car in and after the time window (in which he's already started walking towards the cinema) the system tells him the final income, discount for using the money saving option included.

\subsection{Scenario 10: Recover a car with user input}
	Obi-Wan is driving peacefully to reach his yoga instructor, Qui-Gon Jinn, when the car breaks down; he tries to restart it or check what is wrong, but the system doesn't detect any anomaly and he isn't a mechanic, so he decides to notify the company: he opens the app on his phone and enters the \textit{Emergency help} section. The app asks him to broadly describe the problem by filling a form. He then selects the option "car doesn't work" and the system tells him that an operator is on his way. In the meantime the system, having located the car, notifies the admin of its whereabouts. The admin checks which operator is closest to the site and available and sends him. The operator – which is also a mechanic – checks the car on site and then, since the car needs more serious repairs, he notifies the admin that the reparation cannot be carried out on-site. While the admin dispatches another operator with a tow truck, the system informs Obi-Wan of the final charges (calculated until the notification of the breakdown). The car is no longer his. 
	The new operator arrives and tows the car to the company's garage. She contacts the insurance company, that comes and checks the car. The insurance decides the breakdown was not Obi-Wan's fault, and pays the cost of the repairs.
	
\subsection{Scenario 11: Manually assist parked car}
	An unnamed user has left a car with <3\% battery in a safe area far from the power grid. The system locates the car and alerts an admin of the situation. The admin locates the operator with a tow truck closest to the site and assigns the maintenance to him. The operator was free so he accepts and reaches the car. He tows it to the nearest recharging area and plugs it there. The operator then notifies the system that he completed the maintenance operation.