	\subsection{Program Stubs and Drivers}
	
	As we mentioned in \autoref{sec:integration_testing_strategy}, we are going to use a bottom-up approach to integrate and test all macro-components of the system. This means that on the one hand we need a series of drivers to perform the method invocations while the higher-level components still haven't been developed. On the other hand, while it's true that in general we don't need stubs since the lower-level components will have been developed before testing the following level, in \autoref{sec:integration_testing_strategy} we specified that three macro-components needed a critical-first approach: these are the \textbf{Money Saving Option Manager}, the \textbf{Car Manager} and the \textbf{Payment Manager}. In the developing of these components we will start by integrating the most critical subcomponent and then the remaining ones. For these reason, the \textbf{Car Manager} integration and the \textbf{Money Saving Option Manager} integration will require drivers (since their critical component is the most low-level one); on the contrary, the \textbf{Payment Manager} will require the definition of stubs to simulate the potential invoked functions.
	For the specifics of each method invocation performed by the drivers, please refer to \autoref{sec: individual_steps}.
		
		\subsubsection{Stubs}
		\label{sec:stubs}
			For the \textbf{Invoice Manager} integration we will need some program stubs:
			\begin{itemize}
				\item \textbf{Payment Handler Stub}: this testing module will emulate the invoked functions belonging to the \textbf{Payment Handler} subcomponent.
				\item \textbf{Exceptional Payment Handler stub}: this testing module will emulate the invoked functions belonging to the \textbf{Exceptional Payment Handler} subcomponent.
			\end{itemize} 	

		
		
		\subsubsection{Drivers}
		\label{sec:drivers}

		Here follows a list of drivers needed by the system to perform testing according to our strategy. Following the bottom-up approach, drivers for subcomponents will be provided when needed as well as drivers emulating macro-components.
		
		\begin{description}
		\item[Localisation Manager]~\\
			\begin{itemize}
				\item \textbf{Localization Driver}: this testing module will invoke the methods exposed by the \textbf{Localization Manager} component.
			\end{itemize}
		\item[User Manager]~\\ 
			\begin{itemize}
				\item \textbf{User Handler Driver}: this testing module will invoke the methods exposed by the \textbf{User Handler} subcomponent.
				\item \textbf{License Manager Driver}: this testing module will invoke the methods exposed by the \textbf{License Manager} subcomponent.
				\item \textbf{Profile Manager Driver}: this testing module will invoke the methods exposed by the \textbf{Profile Manager} subcomponent.
				\item \textbf{User Manager Driver}: this testing module will invoke the methods exposed by the \textbf{User Manager} component.
			\end{itemize}
		\item[Car Manager]~\\
			\begin{itemize}
				\item \textbf{Car Handler Driver}: this testing module will invoke the methods exposed by the \textbf{Car Handler} subcomponent.
				\item \textbf{Car Manager Driver}: this testing module will invoke the methods exposed by the \textbf{Car Manager} component.
			\end{itemize}
		\item[Parking Manager]~\\
			\begin{itemize}
				\item \textbf{Parking Manager Driver}: this testing module will invoke the methods exposed by the \textbf{Parking Manager} component.
			\end{itemize}
		\item[Access Manager]~\\ 
			\begin{itemize}
				\item \textbf{Registration Driver}: this testing module will invoke the methods exposed by the \textbf{Registration} subcomponent.
				\item \textbf{Login Driver}: this testing module will invoke the methods exposed by the \textbf{Login} subcomponent.
				\item \textbf{Access Manager Driver}: this testing module will invoke the methods exposed by the \textbf{Access Manager} component.
			\end{itemize}
		\item[MSO Manager]~\\
			\begin{itemize}
				\item \textbf{Parking Distribution Driver}: this testing module will invoke the methods exposed by the \textbf{Parking Distribution Handler} subcomponent.
				\item \textbf{MSO Driver}: this testing module will invoke the methods exposed by the \textbf{MSO Manager} component.
			\end{itemize}
		\item[Car Employment Manager]~\\
			\begin{itemize}
				\item \textbf{Time Manager Driver}: this testing module will invoke the methods exposed by the \textbf{Time Manager} subcomponent.
				\item \textbf{Reservation Driver}: this testing module will invoke the methods exposed by the \textbf{Reservation Handler} subcomponent.
				\item \textbf{Employment Driver}: this testing module will invoke the methods exposed by the \textbf{Car Employment Manager} component.
			\end{itemize}
		\item[Maintenance Manager]~\\
			\begin{itemize}
				\item \textbf{Report Status Driver}: this testing module will invoke the methods exposed by the \textbf{Report Status Handler} subcomponent.
				\item \textbf{Report Driver}: this testing module will invoke the methods exposed by the \textbf{Emergency Report Handler} subcomponent.
				\item \textbf{Operators Driver}: this testing module will invoke the methods exposed by the \textbf{Operators Handler} subcomponent.
				\item \textbf{Maintenance Driver}: this testing module will invoke the methods exposed by the \textbf{Maintenance Manager} component.
			\end{itemize}	
		\item[BackEnd Manager]~\\
			\begin{itemize}
				\item \textbf{Backend Driver}: this testing module will invoke the methods exposed by the \textbf{BackEnd Manager} subcomponent.
			\end{itemize}
		\item[Payment Manager]~\\ 
			\begin{itemize}
				\item \textbf{Payment Handler Driver}: this testing module will invoke the methods exposed by the \textbf{Payment Handler} subcomponent.
				\item \textbf{Dicounts and Sanctions Handler Driver}: this testing module will invoke the methods exposed by the \textbf{Dicounts and Sanctions Handler} subcomponent.
				\item \textbf{Exceptional Handler Driver}: this testing module will invoke the methods exposed by the \textbf{Exceptional Payment Handler} subcomponent.
				\item \textbf{Invoice Manager Driver}: this testing module will invoke the methods exposed by the \textbf{Invoice Manager} subcomponent.
				\item \textbf{Payment Manager Driver}: this testing module will invoke the methods exposed by the \textbf{Payment Manager} component.
			\end{itemize}
		
		\end{description}
		
	
	
	
	\subsection{Test Data}
	
	In order to perform the tests specified in \autoref{sec: individual_steps} we will need a range of test data, both valid and invalid. This chapter will list those data in reference to the specific set of macro-components that will need them.
	
		\input{subsections/program_stubs_1.tex}
	
		\subsubsection{Employment}
		
		\begin{itemize}
			\item A list of valid and invalid \textbf{Reservations}. The set should contain instances exhibiting the following cases:
				\begin{itemize}
					\item Null object
					\item Null fields
					\item Reservation expired
					\item Starting time for the reservation set in the future
					\item Reservation on a car that is being used
					\item Reservation on a nonexistent car
				\end{itemize}
		\end{itemize}
		
		\begin{itemize}
			\item A list of valid and invalid \textbf{Rides}. The set should contain instances exhibiting the following cases:
				\begin{itemize}
					\item Null object
					\item Null fields
					\item Ride that has already ended
					\item Ride on a car that is already being used
					\item Ride on a nonexistent car
					\item Ride associated with a user already using another car
				\end{itemize}
		\end{itemize}
		
		\begin{itemize}
			\item A list of valid and invalid \textbf{ParkingAreas}. The set should contain instances exhibiting the following cases:
				\begin{itemize}
					\item Null object
					\item Null fields
					\item ParkingAreas containing a car that is located somewhere else
					\item ParkingArea outside city boundaries
					\item ParkingArea with more parked cars than slots
					\item Full ParkingArea
					\item Empty ParkingArea
				\end{itemize}
		\end{itemize}
		
		
		
		\subsubsection{Money Saving Option}
		
		\begin{itemize}
			\item A list of valid and invalid \textbf{destinations}. The set should contain instances exhibiting the following cases:
				\begin{itemize}
					\item Null object
					\item Null fields
					\item Destination is outside city boundaries
					\item Destination has no parking areas within the radius requested by the MSO
					\item Destination doesn't exist
					\item Destination is the car's current location
				\end{itemize}
		\end{itemize}
		
		
		
		\subsubsection{Backend}
		
		\begin{itemize}
			\item A list of valid and invalid \textbf{Parameters}. The set should contain instances exhibiting the following cases:
				\begin{itemize}
					\item Null object
					\item Null fields
					\item Parameter value outside allowed range
				\end{itemize}
		\end{itemize}
		
		\begin{itemize}
			\item A list of valid and invalid \textbf{Emergency Reports}. The set should contain instances exhibiting the following cases:
				\begin{itemize}
					\item Null object
					\item Null fields
					\item Report closed
					\item Report without User assigned
					\item Report without Car assigned
					\item Report without Operator assigned
					\item Report with an available Operator assigned
				\end{itemize}
		\end{itemize}
