In this section we will use the COCOMO II approach in order to estimate the cost and effort required by \textit{PowerEnJoy}'s development. \\

We will use the results drawn in \autoref{sec:FP} and the estimated Source Lines of Code to use as values in COCOMO II equations. To decide on the values of scale factors and cost drivers, we will refer to the official COCOMO II manual (see \autoref{sec:references} for hyperlink and further detail). The reference tables will be re-drawn for readability in each section, referencing them as \textit{"CII modelman"}.\\

The following equations will be used to calculate the effort (in persons month) and duration (in months) of our project:

		\paragraph{}\(Effort = A \times EAF \times KSLOC^E\)\\
wherein
		\paragraph{}\(E = B + 0.01 \times \sum_{j=1}^{5}SF_j\)\\
is the exponent (B is a constant that in COCOMO II has value $B=0.91$), A is a constant that in COCOMO II has value $A=2.94$, and
		\paragraph{}\(EAF = \prod_{i=1}^{17}CD_i \).\\

For the duration, we will use the following formula:
		\paragraph{}\(Duration = C \times Effort^F\)\\
where $C=3.67$ and
		\paragraph{}\(F = D + 0.2 \times (E - B) = 0.28 + 0.2 \times ( E - 0.91 )\).


\subsubsection{Scale Factors}

Scale factors (SF) are used to "account for the relative economies or diseconomies of scale encountered for software projects of different sizes" [Banker et al. 1994]. They are used to calculate the exponent E and there are five of them:\\

\begin{center}
	\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
		\multicolumn{7}{c}{\textbf{Scale Factor values, $SF_j$}}\\
		\hline
		\textbf{Scale Factors} & \textbf{Very Low} & \textbf{Low} & \textbf{Nominal} & \textbf{High} & \textbf{Very High} & \textbf{Extra High}\\ \hline
		
		\textbf{PREC} & thoroughly unprecedented & largely unprecedented & somewhat unprecedented & generally familiar & largely familiar & thoroughly familiar \\
		$SF_j$ & 6.20 & 4.96 & 3.72 & 2.48 & 1.24 & 0.00\\ \hline
		
		\textbf{FLEX} & rigorous & occasional relaxation & some relaxation & general conformity & some conformity & general goals\\
		$SF_j$ & 5.07 & 4.05 & 3.04 & 2.03 & 1.01 & 0.00\\ \hline
		
		\textbf{RESL} & little (20\%) & some (40\%) & often (60\%) & generally (75\%) & mostly (90\%) & full (100\%)\\
		$SF_j$ & 7.07 & 5.65 & 4.24 & 2.83 & 1.41 & 0.00\\ \hline
		
		\textbf{TEAM} & very difficult interactions & some difficult interactions & basically cooperative interactions & largely cooperative & highly cooperative & seamless interactions\\
		$SF_j$ & 5.48 & 4.38 & 3.29 & 2.19 & 1.10 & 0.00\\ \hline
		
		\textbf{PMAT} & Level 1 Lower & Level 1 Upper & Level 2 & Level 3 & Level 4 & Level 5\\
		$SF_j$ & 7.80 & 6.24 & 4.68 & 3.12 & 1.56 & 0.00\\ \hline
	\end{tabular}
\end{center}


Here is an explanation of each Scale Factor and our choices:

\begin{itemize}
	\item \textbf{PREC}: Precedentedness describes "if a product is similar to several previously developed projects"\footnote{CII modelman, page 18}. While on the one hand we have no experience with this kind of system, it is also true that we won't need particular innovation and that similar system have been developed before. For these reasons, this factor is set to \textbf{Nominal}.
	\item \textbf{FLEX}: Flexibility describes the need for the software to conform to pre-established requirements and law. This factor is set to \textbf{Very Low}, meaning we have close to no flexibility in regards of either our requirements or state law regarding car driving and payments. Some (very) occasional relaxation may occur in the development of the company requirements. 
	\item \textbf{RESL}: Architecture/Risk Resolution describes our awareness and preparedness with respect to risks; in particular it focuses on architecture and how much interest it has been given to its design and its uncertainties. We believe we have analysed as best as possible the risks inherent to our architecture, hence the value is set to \textbf{High}.
	\item \textbf{TEAM}: Team Cohesion accounts for "the sources of project turbulence and entropy because of difficulties in synchronizing the project’s stakeholders"\footnote{CII modelman, page 20}. We believe our team is cohesive, although it presents a language barrier problem. So this factor is set to \textbf{Very High}.
	\item \textbf{PMAT}: We believe that our inexperience in this kind of project allows for a pretty low project maturity. On the other hand we had only little problems during the planning stages of the project. To account for both those aspects, we set the value of this factor to \textbf{Low}. 
\end{itemize}


To sum up our decisions, here is the following summary table:\\

\begin{center}
	\begin{tabular}{|l|l|l|}
		\hline
		\textbf{Scale Driver} & \textbf{Factor} & \textbf{Value}\\ \hline
		
		PREC & Nominal & 3.72\\
		FLEX & Very Low & 5.07\\
		RESL & High & 2.83\\
		TEAM & Very High & 1.10\\
		PMAT & Low & 6.24\\ \hline
		\multicolumn{2}{|l|}{Total:} & 18.96\\ \hline
	\end{tabular}
\end{center}



\subsubsection{Post-Architecture Cost Drivers}
There are seventeen post-architecture cost drivers, which are multipliers used in COCOMO II in order to adjust the "nominal" effort in person-months in order to take into consideration the software under development. Nominal effort is defined as the effort estimated only using scale factors. 

	\subsubsection*{Product Factors}
	Product factors are needed to account for the variations in the effort required caused by the characteristics of the software under development. There are five of them:
	
	
	
		\begin{itemize}
			\item \textbf{RELY}: RELY measures the "extent to which the software must perform its intended
function over a period of time"\footnote{CII modelman, page 25}. We decided to set it to \textbf{High} in order to keep into consideration the potential finantial losses caused by an accident in the car (even though the car itself is not driven by the system, a failure in notifying some problems with it may have undesired effects) and consequent risks to the driver. 
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{RELY Descriptors} & slight inconvenience & low, easily recoverable losses & moderate, easily recoverable losses & high financial loss & risk to human life & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 0.82 & 0.92 & 1.00 & 1.10 & 1.26 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{DATA}: this cost driver tries to "capture the effect large test data requirements have on
product development"\footnote{CII modelman, page 26}. It is determined by calculating D/P, i.e. the size of the test database in bytes on the SLOC of the program. We have estimated our test database to be in the order of magnitude of 10 megabytes ($10^7 bytes$). Even if we count our SLOC with the average estimation of $\sim 9K SLOC$, the result is greater than 1000. Hence, the value of the cost driver DATA for us is \textbf{Very High}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{DATA Descriptors} & & $D/P < 10 $ & $ 10 \leq D/P < 100$ & $ 100 \leq D/P < 1000$ & $DP \geq 1000$ & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & n/a & 0.90 & 1.00 & 1.14 & 1.28 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{CPLX}: Product Complexity is evaluated based on 5 factors, which are control operations, computational operations, device-dependent operations, data management operations, user interface management operations. Since we expect to have fairly complex operations concerning computation, devices, data management and user interface management, the complexity is set to \textbf{High}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 0.73 & 0.87 & 1.00 & 1.17 & 1.34 & 1.74\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{RUSE}: RUSE means Developed for Reusability. This cost driver was set to \textbf{Nominal} since we probably won't need the additional effort required to develop components for reusability outside of the project itself.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{RUSE Descriptors} & & none & across project & across program & across product line & across multiple product lines\\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & n/a & 0.95 & 1.00 & 1.07 & 1.15 & 1.24\\ \hline
			\end{tabular}
		\end{center}
		
		
		

		\begin{itemize}
			\item \textbf{DOCU}: the DOCU cost driver accounts for the dimensioning of the documentation with respect to the life-cycle needs. This driver is set to very low if the documentation is next to none and very high if the documentation is excessive. We set this value to \textbf{Nominal}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{DOCU Descriptors} & Many life-cycle needs uncovered & Some life-cycle needs uncovered & Right-sized to life-cycle needs & Excessive for life-cycle needs & Very excessive for life-cycle needs & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 0.81 & 0.91 & 1.00 & 1.11 & 1.23 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
	
	
	\subsubsection*{Platform Factors}
	Platform Factors take in consideration the complexity of hardware and infrastructure software needed for the system. 
	
	
		\begin{itemize}
			\item \textbf{TIME}: the TIME factor measures the Execution Time Constraint imposed upon a software system. Since \textit{PowerEnJoy} is quite a complex system, we expect a high execution time needed; on the other hand, our intention is to choose the dimentions of the CPU so that our system will use 85\% of available execution time at operating time. For this reason the value is set to \textbf{High}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{TIME Descriptors} & & & $\leq$50\% use of available execution time & 70\% use of available execution time & 85\% use of available execution time & 95\% use of available execution time\\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & n/a & n/a & 1.00 & 1.11 & 1.29 & 1.63\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{STOR}: it represents the degree of Main Storage Constraint imposed on a system. Having a relatively small test database and being commercially available many storage units that can contain Terabytes of data, we don't believe storage will be a serious matter for us. Hence, this driver is set to \textbf{Nominal}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{STOR Descriptors} & & & $\leq$50\% use of available storage & 70\% use of available storage & 85\% use of available storage & 95\% use of available storage\\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & n/a & n/a & 1.00 & 1.05 & 1.17 & 1.46\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{PVOL}: The PVOL accounts for the volatility of the platforms on which the system is deployed. We believe that the clients operating systems may perform major updates than once a year; it is also true that we don't expect our other platforms to change often. For these reasons, we decided to set the PVOL value to \textbf{Nominal}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{PVOL Descriptors} & & Major change every 12 mo.; minor change every 1 mo. & Major: 6 mo; minor: 2 wk. & Major: 2 mo; minor: 1 wk. & Major: 2 wk.; minor: 2 days & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & n/a & 0.87 & 1.00 & 1.15 & 1.30 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
	
	\subsubsection*{Personnel Factors}
	These cost drivers try to consider the personnel's abilities, experience and skills to put into the effort estimation. These are some of the most influential cost drivers, since the team's productivity and experience considerably changes the effort required to develop a project. 
	
	
		\begin{itemize}
			\item \textbf{ACAP}: ACAP evaluates the capabilities of analysts, i.e. people working on requirements and design. The attributes to consider while evaluating ACAP are thoroughness, efficiency, ability, and the will to communicate and cooperate. We believe our team has worked well while drawing up requirements and deciding the design for the system, so we set this factor to \textbf{High}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{ACAP Descriptors} & 15th percentile & 35th percentile & 55th percentile & 75th percentile & 90th percentile & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.42 & 1.19 & 1.00 & 0.85 & 0.71 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{PCAP}: PCAP evaluates the capabilities of the programmers as a team. The experience of the programmers is not rated here, since that will be evaluated later; factors to be considered during the evaluation are instead ability, thoroughness, efficiency and cooperation. Our team is cohesive and hard-working, but we believe that, since we're students, we may be lacking some knowledge and abilities. Hence this value is set to \textbf{Nominal}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{PCAP Descriptors} & 15th percentile & 35th percentile & 55th percentile & 75th percentile & 90th percentile & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.34 & 1.15 & 1.00 & 0.88 & 0.76 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{PCON}: Personnel Continuity stands for the annual turnover of personnel working on the project. We set it to \textbf{Very High} since we don't expect we will ask new people to help us or that some of us will leave the project.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{PCON Descriptors} & 48\% / year & 24\% / year & 12\% / year & 6\% / year & 3\% / year & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.29 & 1.12 & 1.00 & 0.90 & 0.81 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{APEX}: this cost driver evaluates the experience that the project team has with similar types of applications. We've never worked on similar projects before, neither with regards to the domain (i.e. car rentals) nor with its scope and dimentions; on the other hand we've been acquainting ourselves with the project system itself for the past few months, so we've decided to set this value to \textbf{Low}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{APEX Descriptors} & $\leq$ 2 months & 6 months & 1 year & 3 years & 6 years & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.22 & 1.10 & 1.00 & 0.88 & 0.81 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{PLEX}: PLEX evaluates the same thing as APEX, but with respect to the platforms instead of the application. The team has been acquainting itself with the clients operating system, the cars' management system and so on for the duration of the project, and for this reason we set this cost driver to \textbf{Low}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{PLEX Descriptors} & $\leq$ 2 months & 6 months & 1 year & 3 years & 6 years & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.19 & 1.09 & 1.00 & 0.91 & 0.85 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
		\begin{itemize}
			\item \textbf{LTEX}: LTEX evaluate the languages and tools experience the team has. We are all fairly acquainted with Java and DBMS languages; however we'd never worked with JEE before, nor with the tools related to it, so we set this value to \textbf{Nominal}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{LTEX Descriptors} & $\leq$ 2 months & 6 months & 1 year & 3 years & 6 years & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.20 & 1.09 & 1.00 & 0.91 & 0.84 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		
	\subsubsection*{Project Factors}
	This set of cost drivers account for the use of modern software tools, location of the development team, compression of the project schedule. 
	
		\begin{itemize}
			\item \textbf{TOOL}: the TOOL rating changes based on the complexity, efficiency and timeliness of the development tools used. We have been using the most updated tools available open source, so this value is set to \textbf{Very High}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{TOOL Descriptors} & edit, code, debug & simple frontend, backend, CASE, little integration & basic life-cycle tools, moderately integrated & strong, mature life-cycle tools, moderately integrated & strong, mature, proactive life-cycle tools, well integrated with processes, methods, reuse & \\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.17 & 1.09 & 1.00 & 0.90 & 0.78 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
		
		\begin{itemize}
			\item \textbf{SITE}: SITE accounts on the collocation and communication support between teams (or team members, in our case). We all live in the same city and use occasional audio conferences and in general wide band electronic communication, so we set this driver to \textbf{High}.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{SITE: Collocation Descriptors} & International & Multi-city and multi-company & Multi-city or multi-company & Same city or metro area & Same building or complex & Fully collocated \\ \hline
				
				\textbf{SITE: Communications Descriptors} & some phone, mail & Individual phone, FAX & Narrow band email & Wideband electronic communication & Wideband electronic communication, occasional video conf. & Interactive multimedia\\ \hline
			
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.22 & 1.09 & 1.00 & 0.93 & 0.86 & 0.80\\ \hline
			\end{tabular}
		\end{center}
		
		

		
		\begin{itemize}
			\item \textbf{SCED}: this rating "measures the schedule constraint imposed on the project team developing the
software"\footnote{CII modelman, page 34}. This value is set to \textbf{High}, because while we tried as much as possible to distribute the developing process, it is also true that the team members had other obligations with the university. So the compression of the schedule was high.
		\end{itemize}
		
		\begin{center}
			\begin{tabular}{ | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | C{2cm} | }
				\hline
				\textbf{SCED Descriptors} & 75\% of nominal & 85\% of nominal & 100\% of nominal & 130\% of nominal & 160\% of nominal & \\ \hline
				
				\textbf{Rating levels} & Very Low & Low & Nominal & High & Very High & Extra High\\ \hline
			
				\textbf{Effort multipliers} & 1.43 & 1.14 & 1.00 & 1.00 & 1.00 & n/a\\ \hline
			\end{tabular}
		\end{center}
		
		
\vspace{2cm}


Our results are expressed in the summary table below: 


	\begin{center}
		\begin{tabular}{|l|l|l|}
			\hline
			\textbf{Scale Driver} & \textbf{Factor} & \textbf{Value}\\ \hline
		
			RELY & High & 1.10\\
			DATA & Very High & 1.28\\
			COMPLEXITY & High & 1.17\\
			RUSE & Nominal & 1.00\\
			DOCU & Nominal & 1.00\\ \hline
			
			TIME & Very High & 1.29\\
			STOR & Nominal & 1.00\\
			PVOL & Nominal & 1.00\\ \hline
			
			ACAP & High & 0.85\\
			PCAP & Nominal & 1.00\\
			PCON & Very High & 0.81\\
			APEX & Low & 1.10\\
			PLEX & Low & 1.09\\
			LTEX & Nominal & 1.00\\ \hline
			
			TOOL & Very High & 0.78\\
			SITE & High & 0.93\\
			SCED & High & 1.00\\ \hline	
			
			\multicolumn{2}{|l|}{Total (multiplication):} & 1.27256\\ \hline
		\end{tabular}
	\end{center}
	
	
	\subsubsection{Final results}
	
	Basing ourselves on the values calculated above and on the equations shown at the beginning of the chapter, these are our final results: \\
	
	\paragraph{}\(E = B + 0.01 \times \sum_{j=1}^{5}SF_j = 0.91 + 0.01 \times 18.96 = 1.0996\)\\
	
	\paragraph{}\(EAF = \prod_{i=1}^{17}CD_i = 1.27256\)\\
	
	\paragraph{}\(Effort_{\text{avg}} = A \times EAF \times KSLOC^E\ = 2.94 \times 1.27256 \times (9.338)^{1.0996} = 43.64 PM = 44 PM\)\\
	
	\paragraph{}\(Effort_{\text{high}} = A \times EAF \times KSLOC^E\ = 2.94 \times 1.27256 \times (13.601)^{1.0996} = 65.99 PM = 66 PM\)\\

	\paragraph{}\(F = D + 0.2 \times (E - B) = 0.28 + 0.2 \times ( 1.0996 - 0.91 ) = 0.31792\)\\
	
	\paragraph{}\(Duration_{\text{avg}} = C \times Effort^F = 3.67 \times 44PM^{0.31792} = 12.22 months\)\\
	
	\paragraph{}\(Duration_{\text{high}} = C \times Effort^F = 3.67 \times 66PM^{0.31792} = 13.90 months\)\\