\subsection{Purpose and scope}
	The present document is the \textbf{Project Plan Document} for the \textit{PowerEnJoy} system. It aims to analyse the dimension of the project and the effort required, to guide and assist the management of all the involved processes. \newline
	In \textbf{section 2}, a post-architecture analysis of the dimension and effort cost of the project is performed. An estimate of the source lines of code (SLOC) is computed applying the Function Point (FP) approach. Subsequently, this evaluation is used to predict the actual effort the project will require, using the COCOMO II framework. The result can be used as a reference parameter to update the budget evaluation and provide an estimate of the resource allocation.\newline
	\textbf{Section 3} and \textbf{section 4} take into account the effort estimation to provide a possible schedule and a human resource allocation for the project.\newline
	Finally, \textbf{section 5} conducts an analysis of the most critical risks the project may face, trying to describe the preventive contingency plans to be adopted.

\subsection{Definitions, acronyms, abbreviations}
	Provided here is a short list of acronyms often used inside this document. Please refer to the previous documents’ chapter on definitions and abbreviations for any term not described here.
	\subsubsection{Acronyms}
		\begin{itemize}
			\item \textbf{SLOC}: Source Lines Of Code, a software metric used to measure the size of a system.
			\item \textbf{FP}: Function Points, a size estimation method for software.
			\item \textbf{COCOMO}: COnstructive COst MOdel, a software cost estimation model. In this document, the evolution COCOMO II is used.
		\end{itemize}

\subsection{Reference documents}
\label{sec:references}
	Here is provided a list of documents we used as reference.
	\begin{description}
		\item[PowerEnJoy RASD]: the Requirement Analysis and Specification Document for \textit{PowerEnJoy}'s system.
		\item[PowerEnJoy DD]: the Design Document for \textit{PowerEnJoy}'s system.
		\item[Project Assignment]: the project assignment document, \textit{Assignments AA 2016-2017.pdf}.
		\item[\url{http://www.softwaremetrics.com/fpafund.htm}] A FP guide.
		\item[\url{http://www.qsm.com/resources/function-point-languages-table}] The QSM Function Points Languages Table, containing the function point language gearing factors.
		\item[\url{http://csse.usc.edu/csse/research/COCOMOII/cocomo2000.0/CII\_modelman2000.0.pdf}] The COCOMO II Model Definition Manual.
	\end{description}
